Sheafification in HoTT

### 2015-01-10 paper/sheaf_lics.tex
paper

\usepackage{wasysym}
\usepackage[all]{xy}
\def\dar[#1]{\ar@<2pt>[#1]\ar@<-2pt>[#1]}
\DeclareMathOperator{\Type}{Type}
\DeclareMathOperator{\HProp}{HProp}
\newcommand{\modal}{\ensuremath{\ocircle}}

@@

\section{Homotopy Type Theory}
\label{sec:homotopy-type-theoryhott}

@@

We refer to~\cite{hottbook}.

@@

We use the following definition of truncated left exact modalities~:
\begin{defi}
  Let $p$ be a truncation index. Then a left exact modality is the
  data of
  \begin{itemize}
  \item A predicate $P~:~\Type_p \to \HProp$
  \item For every $p$-truncated type $A$, a $p$-truncated type
    $\modal A$ such that $P(\modal A)$
  \item For every $p$-truncated type $A$, a map $\eta_A~:~A \to
    \modal A$
  \end{itemize}
  such that
  \begin{itemize}
  \item For every $p$-truncated types $A$ and $B$, if $P(B)$ then
    $$\left\{
      \begin{array}{rcl}
        (\modal A \to B) & \to & (A \to B) \\
        f & \mapsto & f \circ \eta_A
      \end{array} \right.$$
    is an equivalence.
  \item For all $A~:~\Type_p$ and $B~:~A \to \Type_p$ such that $P(A)$
    and $\Pi_{x:A} P(B x)$, then $P\left( \Sigma_{x:A} B(x)\right)$
  \item For all $A~:~\Type_p$ and $x,y~:~A$, if $\modal A$ is
    contractible, then $\modal (x=y)$ is contractible.
  \end{itemize}
\end{defi}

All theorem in~\cite{hottbook}, chapter 7.7 remains true + fibers
preservation :

for all $n$-truncated types,
  and all map $f~:~X \to Y$, the modalisation of fiber of $f$ above any element $y:Y$
  is the fiber of $\modal f$ above $\eta y$~:
  $$\modal \{x:X ~\&~ f~ x = y\} = \{x:\modal X ~\&~ \modal f ~x = \eta_Y
  y\}.$$

  We want moreover that the following diagram commute
  $$\xymatrix{
    \{x:X ~\&~ f~ x = y\} \ar[r]^\eta \ar[d]_\gamma & \modal \{x:X ~\&~ f~ x = y\} \ar@{=}[dl]\\
    \{x:\modal X ~\&~ \modal f ~x = \eta_Y y\} &
  }$$
  where $\Pi_1 \circ \gamma = \eta_X$, and $\Pi_2 \circ \gamma$ is the
  usual modalisation of paths.

\subsection{Generalized pullbacks}
\label{sec:gener-pb}

\begin{itemize}
\item definition
\item giraud axiom
\end{itemize}

\section{Sheaves}

We try to define sheaves inductively~: we define sheaves in $\HProp$
as the classical types ({\em ie} implied by their double negation), and
we define sheaves on $\Type_{n+1}$ {\em via} usual definition of sheaves,
as seen in~maclanemoerdijk and sheaves on $\Type_n$. Of course,
the definition must be cumulative.

@@

\subsection{Definitions and forst properties}
\label{sec:def}

@@

@@

\item If $a,b~:~T~: \Type_{n+1}$ such that $\mu_T a = \mu_T b$, then
  $\modal (a=b)$.

@@

\begin{itemize}
\item 
\begin{thm}
  Any type $A~:~\Type_{n+1}$ closed in a sheaf is itself a sheaf.
\end{thm}

\item Definition of sheafification reflextive subuniverse $(\star,~\nu)$
\end{itemize}

@@

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{3}

@@

>>>>

\usepackage{enumerate}
\usepackage{wasysym}
\usepackage[all]{xy}
\def\dar[#1]{\ar@<2pt>[#1]\ar@<-2pt>[#1]}
\DeclareMathOperator{\Type}{Type}
\DeclareMathOperator{\HProp}{HProp}
\DeclareMathOperator{\nat}{nat}
\DeclareMathOperator{\Unit}{Unit}
\newcommand{\modal}{\ensuremath{\ocircle}}

@@

Plan of the paper~:
\begin{itemize}
\item In section~\ref{sec:hott}, we define the foundations on which
  our worked is based.
\item In section~\ref{sec:sheaves}, we explain the construction of the
  sheafification functor.
\item Finally, we discuss related works and present future works.
\end{itemize}
\section{Homotopy Type Theory}
\label{sec:hott}

@@

We refer to~\cite{hottbook}.
Truncation levels ?

If $x$ is an object of a product or a sigma type, we denote the $i$-th
projection of $x$ by either $\pi_i x$ or $x_i$.

@@

We use the following definition of truncated left exact modalities~:
\begin{defi}
  Let $p$ be a truncation index. Then a left exact modality is the
  data of
  \begin{enumerate}[(i)]
  \item A predicate $P:\Type_p \to \HProp$
  \item For every $p$-truncated type $A$, a $p$-truncated type
    $\modal A$ such that $P(\modal A)$
  \item For every $p$-truncated type $A$, a map $\eta_A:A \to
    \modal A$
  \end{enumerate}
  such that
  \begin{enumerate}[(i)]
    \setcounter{enumi}{3}
  \item For every $p$-truncated types $A$ and $B$, if $P(B)$ then
    $$\left\{
      \begin{array}{rcl}
        (\modal A \to B) & \to & (A \to B) \\
        f & \mapsto & f \circ \eta_A
      \end{array} \right.$$
    is an equivalence.
  \item For all $A:\Type_p$ and $B:A \to \Type_p$ such that $P(A)$
    and $\Pi_{x:A} P(B x)$, then $P\left( \sum_{x:A} B(x)\right)$
  \item For all $A:\Type_p$ and $x,y:A$, if $\modal A$ is
    contractible, then $\modal (x=y)$ is contractible.
  \end{enumerate}
  Conditions (i) to (iv) define a {\em reflective subuniverse}, (i) to
  (v) a {\em modality}.
\end{defi}

Since basic operations (dependent products, products, sigma types) are
stable for truncation levels, all theorem in~\cite{hottbook}, chapter
7.7 remains true.

Moreover, left exactness implies in particular fibers preservations~:
\begin{prop}
For any $n$-truncated types $X$ and $Y$,
and any map $f:X \to Y$, the modalisation of fiber of $f$ above any element $y:Y$
is the fiber of $\modal f$ above $\eta_Y y$~:
$$\modal \left(\sum_{x:X}  (f x = y)\right) = \sum_{x:\modal X} (\modal f x = \eta_Y y).$$

Moreover the following diagram commute
$$\xymatrix{
  \sum_{x:X} (f x = y) \ar[r]^\eta \ar[d]_\gamma & \modal \left(\sum_{x:X}  (f x = y)\right) \ar@{=}[dl]\\
  \sum_{x:\modal X} (\modal f x = \eta_Y y) &
}$$
where $\pi_1 \circ \gamma = \eta_X$, and $\pi_2 \circ \gamma$ is the
usual modalisation of paths.
\end{prop}
\subsection{Generalized pullbacks}
\label{sec:gener-pb}

\begin{defi}
  Let $f:X \to Y$ be a map, and $p:\nat$. The $p$-pullback of $f$,
  noted $X\times_Y \cdots\times_Y X$ is
  the limit of the diagram
  $$\xymatrix{
    X \ar[rd]^f & \cdots & X \ar[ld]_f \\
      &    Y   &
  }$$
  with $p$ copies of $X$. The $0$-pullback of $f$ is $\Unit$.
\end{defi}

In homotopy type theory, we have 
$$X\times_Y \cdots\times_Y X = \sum_{x:X^n} (f x_1 = f x_2) \land
\cdots \land (f x_{n-1} = f x_n).$$
\begin{defi}
  If $f:X \to Y$ is a map, then the {\em \v{C}ech nerve} of $f$ is the
  diagram
  $$C(f) := \cdots
    X \times_Y X \times_Y X
   \underset{\longrightarrow}{\stackrel{\longrightarrow}{\longrightarrow}}
   X \times_Y X 
\stackrel{\longrightarrow}{\longrightarrow} X$$
with canonical projections.
\end{defi}

The Giraud axiom asserts that, if $f:X\to Y$ is a surjection, then the
colimit of $C(f)$ is $Y$. See~\cite{lurie}.

\section{Sheaves}
\label{sec:sheaves}

We define sheaves by induction on the homotopical truncation level of types
~: we define sheaves in $\HProp$ as the classical types ({\em ie}
implied by their double negation), and
we define sheaves on $\Type_{n+1}$ {\em via} usual definition of sheaves,
as seen in~\cite{maclanemoerdijk} and sheaves on $\Type_n$. Of course,
the definition must be cumulative.

@@

\subsection{Definitions and first properties}
\label{sec:def}

@@

\begin{defi}
  Let $E$ be a type. The {\em closure} of a subobject of $E$ classified by $\chi$
  is the subobject of $E$ classified by $\modal \circ \chi$.

  The subobject of $E$ classified by $\chi$ is said {\em closed in
    $E$} if its closure is itself : $\chi = \modal \circ \chi$.
\end{defi}

\begin{defi}
  Let $E$ be a type, and $\chi:E \to \Type_n$. The subobject $A$ of $E$
  classified by $\chi$ is {\em dense} in $E$ if its $\modal$-closure
  is $E$ seen as a subobject of $E$, {\em ie}
  $$\forall e:E,~ \left(\sum_{e':E} e=e'\right) \simeq (\modal (\chi~e)).$$ 
  Moreover, for all $x:A$ we need the following coherence diagram to
  commute
  $$\xymatrix{
    \sum_{e':A} x = e' \ar@{=}[r] \ar[d]_\iota & (\chi~x) \ar[d]^{\eta_{(\chi~x)}}\\
    \sum_{e':E} x = e' \ar@{=}[r] & \modal (\chi~x)
  }$$
  where $\iota: x \mapsto ({x_1}_1 ; x_2)$.
\end{defi}

It follows from fibers preservation that any $n$-subobject of a type seen as a $n$-subobject
of its closure is closed.

@@

\item If $a,b:T:\Type_{n+1}$ such that $\mu_T a = \mu_T b$, then
  $\modal (a=b)$.

@@

\begin{itemize}
\item 
\begin{thm}
  Any type $A:\Type_{n+1}$ closed in a sheaf is itself a sheaf.
\end{thm}

\item Definition of sheafification reflextive subuniverse
  $(\star,~\nu)$
\item left exactness
\item cumulativity
\end{itemize}

@@

Prove that the Giraud axiom holds in homotopy type theory.

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{4}

@@

\bibitem[HTT]{lurie}
Jacob Lurie
\newblock{\em Higher Topos Theory}

\bibitem[lumsdaine]{lumsdaine}
Lumsdaine
\newblock{Diagrams and limits}
